AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-23 Paper/main.tex
10-23 paper

>>>>

To some extent, the attention module in the AttCRISPR can help us to understand the decisions it makes. 
In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels.

In the following content, when we use the word, global, we are referring to rules thats are common throughout the data set. 
If assumed the method with strong generalization ability, it might mean that these rules is common in the corresponding Cas9 system.
On the other hand, local refers to the rules applicable to a certain sgRNA. 
We believe that the locally interpretable is very helpful in the design and optimization of sgRNA.
\begin{figure*}[!tpb]%figure4
    \centerline{\includegraphics[width=178mm]{spatialattention.eps}}
    \caption{wait2write}\label{fig:06}
\end{figure*}

\subsubsection{Globally interpretable}

At global level, a important question we want AttCRISPR to answer is which nucleotide it prefers at each position on the sequence. 
In fact, \citeauthor{wang2019optimized} has already answered this question in detail with the DeepSHAP method.
Leaving aside nucleotides, just consider the importance of each position, the method of \citeauthor{Liu2019} goes some way to answering this question.

\subsubsection{Locally interpretable}
